Introduction

### 2012-10-25 dissertation/tmpsolutions.tex
advocating void paper fully indexed stores
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@411 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

I find the prospect of writing a first paper to explore these different
extensions to VoID very appealing. I would need to put down some
substantial work on notation, but not intending an very elaborate
theory, which is something that requires \SRL. The paper could discuss
the different approaches above, their merits and drawbacks. After
publishing, I could work with the W3C Semantic Web Interest Group to
get one of the solutions into VoID.

\subsection{Fully indexed stores}

Some time ago, I wrote a partial paper about how fully indexed stores
like Hexastore \cite{hexastore} could easily find the cardinality of
any given triple pattern. It would be interesting to publish that soon
in some form.
